Carrier phase and amplitude estimation using pilots and data

### 2012-05-06 paper.tex
Added theorem statement.  Still needs some work, but is probably on the right track.

>>>>

\begin{theorem}
Let $\{w_i, i \in \ints \}$ be a sequence independent and identically distributed, zero mean, circularly symetric complex random variables with $w_i = \rho_i e^{j\Phi_i}$ such that $h = \prob e^{j\round{\Phi_i}} = \prob e^{j\round{\Phi_1}}$ is a positive real number.  Given $\{y_i, i \in P \cup D\}$ from~\ref{eq:sigmod} let $\hat{a}$ be the least squares estimator of $a_0$.  Let $\hat{a} = \hat{\rho}e^{j\hat{\theta}$ and $a_0 = \rho_0 e^{j\theta_0}$.  Put $L = \abs{P \cup D}$ and assume that $\abs{P}/L \rightarrow p$ and $\abs{D}/L \rightarrow d$ as $L \rightarrow \infty$.  Then:
\begin{enumerate}
\item $\fracpart{\theta_0 - \hat{\theta}} \rightarrow 0$ almost surely as $L \rightarrow \infty$,
\item $\hat{\rho} \rightarrow \rho_0( p + d h )$ almost surely as $L \rightarrow \infty$,
\end{enumerate}
\end{theorem}
